Global adjoint tomography -- Model GLAD-M25\footnote{This paper is dedicated to Dimitri Komatitsch, computational geophysicist extraordinaire, who passed away unexpectedly shortly before its submission.}

### 2019-02-10 main.tex
Updates from Overleaf

\usepackage{graphicx}
\graphicspath{ {./figures} }
\usepackage{subfig}
\usepackage{caption}
\usepackage{floatrow}
\usepackage{amssymb}
\usepackage{commath}
\usepackage{amsmath}
\usepackage[dvipsnames]{xcolor}
\floatsetup[figure]{style=plain,subcapbesideposition=top}
%\usepackage[margin=70mm]{geometry}

@@

In this article we compare the results of our inversion with a number of previous tomographic models.
On a global scale, we present comparisons with model S362ANI$+$M~\citep{moulik2014anisotropic},
which is an updated version of model S362ANI~\citep{s362ani},
the starting model for the GLAD-M15 inversion.
We also consider global shear wavespeed models S40RTS~\citep{ritsema2011s40rts},
TX2015~\citep{TX2015}, SEMUCB-WM1~\citep{french2015broad},
and SL2013sv~\citep{SchaefferLebedev13},
as well as compressional wavespeed models LLNL-G3Dv3 \citep{simmons2012llnl}, GAP-P4~\citep{fukao2013subducted}, and UU-P07~\citep{van2018atlas}.
On the scale of North America
we make comparisons with models US22~\citep{zhu2017radial},
a radially anisotropic model based on adjoint tomography using USArray data from 180 regional earthquakes,
and SL2013NA~\citep{schaeffer2014imaging},
a modification of global model SL2013sv focused on North America.
In Europe we use regional model EU60~\citep{zhu2015seismic} for comparison,
which is based on the assimilation of data from 190 regional earthquakes recorded by more than 700 European seismographic stations.
Finally, in Asia we use regional adjoint tomography model EARA2014~\citep{chen2015multiparameter} as a reference, a model based on data from 227 earthquakes recorded by more than 1,800 stations.

@@

As a continuation of our previous work~\citep{bozdaug2016global},
we used the first-generation model GLAD-M15 as our
starting model.
GLAD-M15 is a 3D transversely isotropic earth model, which combined
3D mantle model S362ANI~\citep{kustowski2008anisotropic}
with 3D crustal model CRUST2.0~\citep{bassin2000current} as its starting model.
In this study,
we continue to use the same transversely isotropic model parametrization.
Instead of relying on crustal corrections,
the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
GLAD-M15 was constructed using a global database of 256 earthquakes.
The first 12 iterations of the GLAD-M15 inversion used three-component seismograms with a shortest period of 27~s,
and the final 3 iterations reduced this further to 17~s.
In this study we also used three-component seismograms with a shortest period of 17~s.

@@

In addition to the 256 earthquakes used for the construction of GLAD-M15, we initially carefully selected 784 additional earthquakes
from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{ekstrom2012global},
resulting in a total number of 1,040 earthquakes.
To ensure a good signal-to-noise ratio on a global scale,
the smallest moment magnitude in the database is set to~5.5,
and to avoid complications associated with source dimension and directivity,
the largest moment magnitude is set to~7.2.

@@

The algorithm inverts for the six elements of the moment tensor
and the centroid location~(latitude, longitude, and depth).
These source inversions are computationally very expensive,
because for each of the 1,040~events nine full 3D forward simulations are required.

@@

The misfit function to be minimized during the iterative inversion process must
be carefully constructed. It will typically involve cross-correlation traveltimes
for body waves and frequency-dependent multitaper phase measurements for surface waves.
Measurements are made in several passbands of three-component seismograms rotated
into vertical, radial, and transverse components, resulting in a number of measurement
categories.
In this study, we consider four passbands, namely, a 17--40~s passband targeting body waves,
two 40--100~s passbands separately targeting body and surface waves,
and a 90--250~s passband targeting longer-period surface waves.
Each passband involves measurements on all three components,
which results in a total of twelve measurement categories.
Although the inversion is designed to minimize the overall misfit,
we will be tracking the misfit reduction in each of the categories to ensure that
the model is improving the fit to the data roughly equally across the board.
One of the biggest challenges in the construction of the misfit function is the
highly uneven distribution of earthquakes --- discussed in Section~\ref{section:earthquakes} --- and seismographic stations,
which must be counterbalanced by geographically weighting the data.
This issue is discussed in detail by~\cite{Ruanetal2018};
in this section we present a brief synopsis.

With these considerations in mind,
the overall misfit, $\Phi$, is defined as follows:
\begin{equation}
\label{eq:misfit}
\Phi = \sum_{s}^{S} \omega_s \sum_{c}^{C} \omega_{c} \sum_{r}^{R_{sc}} \omega_{scr} \sum_{w}^{W_{scr}} \omega_{scrw}\, \chi_{scrw}
\quad ,
\end{equation}
where~$S$ denotes the number of sources, $C$ the number of categories,
$R_{sc}$ the number of receivers recording source~$s$ in category~$c$,
and~$W_{scr}$ the number of measurement windows for source~$s$, category~$c$,
and receiver~$r$.
The misfit for a specific source~$s$, category~$c$, receiver~$r$, and window~$w$ is
\begin{equation}
  \chi_{scrw} = \frac{1}{\Delta\omega}\int_{\omega_1}^{\omega_2} \Big( \frac {\Delta \tau_{scrw}} {\sigma_{scrw}} \Big)^2\, \mathrm{d}\omega
\quad ,
\end{equation}
where~$\Delta \tau_{scrw}$ denotes a multi-taper frequency-dependent phase measurement over the frequency interval~$\Delta\omega=\omega_2-\omega_1$\,,
with associated uncertainties~$\sigma_{scrw}$\,.
For body waves, the window misfit is simply the cross-correlation traveltime anomaly,
$\Delta T_{scrw}$\,, weighted by its standard deviation, i.e., $\chi_{scrw}=(\Delta T_{scrw}/\sigma_{scrw})^2$\,.
As in the source inversions,
the window weights are equal, $\omega_{scrw}=1$\,,
and the category weight, $\omega_c$\,, is the reciprocal of the number of measurements in that
category, $1/C$.
Earthquakes mainly occur along plate boundaries,
and most seismographic  stations are confined to the continents,
which leads to a very uneven distribution of sources and stations,
as illustrated in Figs.~\ref{fig:event_1480} and~\ref{fig:stations}.
Therefore, weighting is crucial in global tomography to balance this uneven sampling
of Earth's interior.
Our source and receiver weighting strategy,
encapsulated by the weights~$\omega_s$ and $\omega_{scr}$\,,
is developed to compensate for uneven spatial sampling.
Following the same strategy as for the receiver weights in the source inversions,
we define source and receiver weights as
\begin{equation}
\omega_{s}^{-1} = N\,\sum_{s'=1}^{S} \exp\left[\mbox{}-\left(\frac{\Delta_{ss'}}{\Delta}\right)^2\right]
\quad ,
\label{eq:source_weights}
\end{equation}
and
\begin{equation}
\omega_{scr}^{-1} = N_{sc}\,\sum_{r'=1}^{R_{sc}} \exp\left[\mbox{}-\left(\frac{\Delta_{rr'}}{\Delta_{sc}}\right)^2\right]
\quad ,
\label{eq:receiver_weights}
\end{equation}
respectively.
Here~$N$ and~$N_{sc}$ are normalization factors,
and~$\Delta_{ss'}$ and~$\Delta_{rr'}$ denote angular distances between source and receiver pairs~$\{s,s'\}$ and~$\{r,r'\}$\,.
The reference angular distances~$\Delta$ and~$\Delta_{sc}$ need to be chosen based on the condition 
numbers of the diagonal weighting matrices defined by Eqns.~(\ref{eq:source_weights}) and~(\ref{eq:receiver_weights}).

@@

We use the same transversely isotropic model parametrization as starting model GLAD-M15.
Such a model is described by the five Love parameters $A$, $C$, $L$, $N$, and $F$~\citep{Love27},
or, alternatively, using the mass density~$\rho$, in terms of the wavespeeds~$\alpha_v=\sqrt{C/\rho}$, $\alpha_h=\sqrt{A/\rho}$, $\beta_v=\sqrt{L/\rho}$, $\beta_h=\sqrt{N/\rho}$ and the dimensionless parameter $\eta=F/(A-2L)$~\citep{PREM,DT98}.
Assuming the radial anisotropy is due to shear anisotropy, these five parameters
may be further reduced to four by introducing the bulk sound speed,
$c=\sqrt{\kappa/\rho}$\,.
Therefore, the final four parameters are $c$, $\beta_v$, $\beta_h$, and $\eta$.

@@

The observed seismograms need to be compared to corresponding synthetic seismograms
for the purpose of making measurements.
The forward simulations are based on the global spectral-element solver
SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02a}, and take a CMT solution, a relevant list
of stations, and the current earth model as input.
The solver is GPU accelerated, and the simulations are performed on the Cray supercomputer ``Titan''
at the OLCF.
To simulate 120~min seismograms with a shortest period of 17~s on 384 NVIDIA
Tesla K20X GPUs takes approximately 10~min of wall clock time.
The calculation of Fr\'echet derivatives at a later stage of the workflow requires
access to snapshots of the forward wavefield as part of the parsimonious storage
algorithm developed by~\cite{KoXiBoPeSaLiTr16},
with rapid I/O facilitated by ADIOS~\citep{liu2014hello}.
For the current simulation setup,
this requires about 1~TB of storage per earthquake,
so for 1,480 earthquakes this adds up to 1.5~PB.
This volume of data is generated during~$\sim6$~hours of simulations.
Based on our experience, ADIOS is capable of achieving~$\sim120$~GB/s
of sustained I/O on OLCF resources.
Given that typical write speeds for modern hard disks are~$\sim100$~MB/s,
it would be extremely difficult to carry out global adjoint tomography without the ADIOS library.

@@

As illustrated in Fig.~\ref{fig:preprocess_workflow}, the preprocessing workflow
includes the following phases.
\begin{enumerate}
  \item Signal processing to remove the instrument response from observed data
    to recover ground displacement. Both observed and synthetic data are bandpass
    filtered, and the horizontal components are rotated to obtain the radial and transverse components of motion.
  \item Window selection on a pair of
    observed and synthetic seismograms. Pyflex (a Python version
    of FLEXWIN by \citet{krischer2015}) is
    used to automatically generate windows where observed and
    synthetic data are sufficiently close to make measurements based on user defined
    criteria.
  \item Cross-correlation traveltime or multi-taper phase measurements in selected windows.
  \item Window sorting and cleaning based on statistical analyses of all measurements to eliminate outliers.
  \item Preliminary adjoint source construction based on the sorted windows.
  \item Calculation and assignment of weights, as discussed in Section~\ref{section:misfit}.
  \item Construction of the final, properly weighted, adjoint sources.
\end{enumerate}

@@

Collectively,
the adjoint simulations are the most expensive stage of the workflow. 
Adjoint simulations take the adjoint sources as input, and generate Fr\'echet
derivatives of the four model parameters as output.
The computational cost of one adjoint simulation is roughly twice ($\sim25$~min) that of
a forward simulation, since the forward wavefield is recalculated for convolution with
the adjoint wavefield during the adjoint simulation,
as discussed in~\cite{KoXiBoPeSaLiTr16}.
Using this procedure,
both the forward and adjoint wavefield are calculated in forward time,
and attenuation is accurately taken into account in both simulations.

@@

Starting model GLAD-M15 was constructed using a database of 256 earthquakes.
For iterations 15--17 of the inversion we used an expanded database of 520 events.
Our focus was to validate and test our software and workflow before scaling up
to a larger database of 1,040 events.
For these iterations we used three period bands, namely,
17--40~s, 40--100~s, and 90--250~s,
and we used a nonlinear conjugate
gradient method to update the model.

@@

The misfit reduction for 17--40~s body waves (Figs.~\ref{fig:misfit}b--d) tapers off by
iteration~21, prompting us to add more earthquakes and change the weighting strategy again by reintroducing 17--40~s surface waves.

@@

In this section we discuss model GLAD-M25 in detail.
We begin with a global overview of the model before concentrating on
specific geographical regions.
We conclude by highlighting various slabs and plumes in the model.
Vertical cross sections are plotted relative to the spherical average of GLAD-M25,
as discussed in Appendix~\ref{sec:1Dmodel}.
For plotting purposes and use in other applications,
an expansion of the model in spherical harmonics and radial B-splines is
discussed in Appendix~\ref{sec:shanalysis}.

@@

The deployment of USArray has dramatically increased data coverage across the
continental United States.
In this section, we compare GLAD-M25 in this region 
with two global models, S362ANI$+$M and S40RTS, and two regional models,
US22~\citep{zhu2017radial} and SL2013NA~\citep{schaeffer2014imaging}.
US22 is a radially anisotropic model based on adjoint tomography using
USArray data from 180 regional earthquakes using 15--50~s
body waves and 25--150~s surface waves.
SL2013NA is a global upper-mantle shear wavespeed model based on multimode
surface waveform tomography primarily focused on North America.

@@

In the 200--400~km depth range, we observe a high wavespeed
anomaly within the Gulf of Mexico, which coincides spatially with the deepest
bathymetry and corresponds to a portion of ancient oceanic
Lithosphere~\citep{muller2008, schaeffer2014imaging}.
A remnant of the Juan de Fuca plate,
with a high wavespeed footprint, is visible at depths of 300~km and 400~km,
where SL2013NA shows a much stronger anomaly.

@@

In the Eastern Mediterranean, there is a distinct fast anomaly beneath the 
Dinarides Mountains, separating the Adria plate from the Pannonian Basin,
indicating subduction of the Adria plate beneath the Eurasian plate.
This anomaly gets sharper at 600~km depth.
Its southern part interacts with the Hellenic slab, which penetrates the mantle
transition zone and extends below 1000km in our model.
We discuss the Hellenic Arc further in Section~\ref{section:slabs}.
The Pannonian Basin is characterized by a low wavespeed
anomaly at depths from 100~km to 250~km.
In this depth range we also see slow wavespeeds beneath Anatolia,
stronger than in the two other global models.

@@

In the south,
Scotia Arc subduction is very distinct in GLAD-M25 at all depths,
but barely observable in other models.
To the north,
Caribbean subduction is clearly discernible in model GLAD-M25 and the two $V_\textrm{P}$ models.

@@

In this section we highlight various subduction systems on Earth.
In Fig.~\ref{fig:subd} we compare GLAD-M25~($V_\textrm{P}$) with two compressional wavespeed models,
namely, GAP-P4~\citep{fukao2013subducted} and UU-P07~\citep{van2018atlas}.
Fig.~\ref{fig:subd}(a) features the Aegean subduction zone. All models show a slab penetrating into the lower mantle beyond a depth of 1,000~km.
Fig.~\ref{fig:subd}(b) shows the South American slab, which, in this cross section, ponds in the shallow lower mantle in all three models, before sinking all the way to the CMB.
Figs.~\ref{fig:subd}(c) and~(d) show cuts across the ancient Farallon slab, which penetrates deeply into the lower mantle.
At depths greater than 1,000~km, 
we see a very strong expression of the slab in model Glad-M25, which is much weaker in the two P models.
The difference may be attributed to increased data coverage thanks to USArray, as well as the use of finite-frequency Fr\'echet derivatives.
Finally, Fig.~\ref{fig:subd}(e) shows subduction beneath the Himalayas.

@@

\begin{acknowledgments}
This research used resources of the Oak Ridge Leadership Computing Facility,
which is a DOE Office of Science User Facility supported under contract DE-AC05-00OR22725.
Additional computational resources were provided by the Princeton Institute
for Computational Science \& Engineering (PICSciE).
We acknowledge IRIS ({\tt iris.edu}) and ORFEUS ({\tt orfeus-eu.org}) for
providing the data used in this study.
We thank Ryan Modrak, Ridvan \"{O}rsvuran, Frederik Simons, and James Smith for fruitful discussions.
The open source spectral-element software package SPECFEM3D\_GLOBE and
the seismic measurement software package FLEXWIN used for this article are
 freely available via the Computational Infrastructure for Geodynamics
 (CIG; {\tt geodynamics.org}). This research was supported by NSF grant~1644826.

\end{acknowledgments}

>>>>

\usepackage{graphicx}
\graphicspath{ {./figures} }
\usepackage{subfig}
\usepackage{caption}
\usepackage{floatrow}
\usepackage{amssymb}
\usepackage{commath}
\usepackage{amsmath}

% colors to show the corrections
\usepackage[dvipsnames,usenames]{xcolor}

% colors to show the corrections
\newcommand{\red}[1]{\textbf{\textcolor{Red}{#1}}}
\newcommand{\blue}[1]{\textbf{\textcolor{Blue}{#1}}}
\newcommand{\cyan}[1]{\textbf{\textcolor{Cyan}{#1}}}
\newcommand{\green}[1]{\textbf{\textcolor{Green}{#1}}}
\newcommand{\magenta}[1]{\textbf{\textcolor{Magenta}{#1}}}
\newcommand{\orange}[1]{\textbf{\textcolor{Orange}{#1}}}

\floatsetup[figure]{style=plain,subcapbesideposition=top}
%\usepackage[margin=70mm]{geometry}

@@

In this article we compare the results of our inversion with a number of previous tomographic models.
On a global scale, we present comparisons with model S362ANI$+$M~\citep{moulik2014anisotropic},
which is an updated version of model S362ANI~\citep{kustowski2008anisotropic},
the starting model for the GLAD-M15 inversion.
We also consider global shear wavespeed models S40RTS~\citep{ritsema2011s40rts},
TX2015~\citep{TX2015}, SEMUCB-WM1~\citep{french2015broad},
and SL2013sv~\citep{SchaefferLebedev13},
as well as compressional wavespeed models LLNL-G3Dv3 \citep{simmons2012llnl}, GAP-P4~\citep{fukao2013subducted}, and UU-P07~\citep{van2018atlas}.
On the scale of North America
we make comparisons with models US22~\citep{zhu2017radial},
a radially anisotropic model based on adjoint tomography using USArray data from 180 regional earthquakes,
and SL2013NA~\citep{schaeffer2014imaging},
a modification of global model SL2013sv focused on North America.
In Europe we use regional model EU60~\citep{zhu2015seismic} for comparison,
which is based on the assimilation of data from 190 regional earthquakes recorded by more than 700 European seismographic stations.
Finally, in Asia we use regional adjoint tomography model EARA2014~\citep{chen2015multiparameter} as a reference, a model based on data from 227 earthquakes recorded by more than 1,800 stations.

@@

As a continuation of our previous work~\citep{bozdaug2016global},
we used the first-generation model GLAD-M15 as our
starting model.
GLAD-M15 is a 3D transversely isotropic earth earth model, which combined
3D mantle model S362ANI~\citep{kustowski2008anisotropic}
with 3D crustal model CRUST2.0~\citep{bassin2000current} as its starting model.
In this study,
we continue to use the same transversely isotropic model parametrization.
Instead of relying on crustal corrections,
the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
GLAD-M15 was constructed using a global database of 253 earthquakes.
The first 12 iterations of the GLAD-M15 inversion used three-component seismograms with a shortest period of 27~s,
and the final 3 iterations reduced this further to 17~s.
In this study we also used three-component seismograms with a shortest period of 17~s.

@@

In addition to the 253 earthquakes used for the construction of GLAD-M15, we initially carefully selected 784 additional earthquakes
from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{ekstrom2012global},
resulting in a total number of 1,040 earthquakes.
To ensure a good signal-to-noise ratio on a global scale,
the smallest moment magnitude in the database is set to~5.5,
and to avoid complications associated with source dimension and directivity,
the largest moment magnitude is set to~7.2.

@@

The algorithm inverts for the six elements of the moment tensor
and the centroid location~(latitude, longitude, and depth).
These source inversions are computationally very expensive,
because for each of the 1,040~events nine full 3D forward simulations are required to obtain the source parameter Fr\'echet derivatives.

@@

The misfit function to be minimized during the iterative inversion process must
be carefully constructed.
In this study,
it typically involves cross-correlation traveltimes
for body waves and frequency-dependent multitaper phase measurements for surface waves.
Measurements are made in several passbands of three-component seismograms rotated
into vertical, radial, and transverse components, resulting in a number of measurement
categories.
In this study, we consider four passbands, namely, a 17--40~s passband targeting body waves,
two 40--100~s passbands separately targeting body and surface waves,
and a 90--250~s passband targeting longer-period surface waves.
Each passband involves measurements on all three components,
which results in a total of twelve measurement categories.
Although the inversion is designed to minimize the overall misfit,
we track the misfit reduction in each of the categories to ensure that
the model is improving the fit to the data roughly equally across the board.
One of the biggest challenges in the construction of the misfit function is the
highly uneven distribution of earthquakes --- discussed in Section~\ref{section:earthquakes} --- and seismographic stations,
which must be counterbalanced by geographically weighting the data.
This issue is discussed in detail by~\cite{Ruanetal2018};
in this section we present a brief synopsis.

With these considerations in mind,
the overall misfit, $\Phi$, is defined as follows:
\begin{equation}
\label{eq:misfit}
\Phi = \sum_{s}^{S} \omega_s \sum_{c}^{C} \omega_{c} \sum_{r}^{R_{sc}} \omega_{scr} \sum_{w}^{W_{scr}} \omega_{scrw}\, \chi_{scrw}
\quad ,
\end{equation}
where~$S$ denotes the number of sources, $C$ the number of categories,
$R_{sc}$ the number of receivers recording source~$s$ in category~$c$,
and~$W_{scr}$ the number of measurement windows for source~$s$, category~$c$,
and receiver~$r$.
The misfit for a specific source~$s$, category~$c$, receiver~$r$, and window~$w$ is
\begin{equation}
  \chi_{scrw} = \frac{1}{\Delta\omega}\int_{\omega_1}^{\omega_2} \Big( \frac {\Delta \tau_{scrw}} {\sigma_{scrw}} \Big)^2\, \mathrm{d}\omega
\quad ,
\end{equation}
where~$\Delta \tau_{scrw}$ denotes a multi-taper frequency-dependent phase measurement over the frequency interval~$\Delta\omega=\omega_2-\omega_1$\,,
with associated uncertainties~$\sigma_{scrw}$\,.
For body waves, the window misfit is often simply the cross-correlation traveltime anomaly,
$\Delta T_{scrw}$\,, weighted by its standard deviation, i.e., $\chi_{scrw}=(\Delta T_{scrw}/\sigma_{scrw})^2$\,.
As in the source inversions,
the window weights are equal, $\omega_{scrw}=1$\,,
and the category weight, $\omega_c$\,, is the reciprocal of the number of measurements in that
category, $1/C$.
Earthquakes mainly occur along plate boundaries,
and most seismographic  stations are confined to the continents,
which leads to a very uneven distribution of sources and stations,
as illustrated in Figs.~\ref{fig:event_1480} and~\ref{fig:stations}.
Therefore, weighting is crucial in global tomography to balance this uneven sampling
of Earth's interior.
Our source and receiver weighting strategy,
encapsulated by the weights~$\omega_s$ and $\omega_{scr}$\,,
is developed to compensate for uneven spatial sampling.
Following the same strategy as for the receiver weights in the source inversions,
we define source and receiver weights as
\begin{equation}
\omega_{s}^{-1} = N\,\sum_{s'=1}^{S} \exp\left[\mbox{}-\left(\frac{\Delta_{ss'}}{\Delta}\right)^2\right]
\quad ,
\label{eq:source_weights}
\end{equation}
and
\begin{equation}
\omega_{scr}^{-1} = N_{sc}\,\sum_{r'=1}^{R_{sc}} \exp\left[\mbox{}-\left(\frac{\Delta_{rr'}}{\Delta_{sc}}\right)^2\right]
\quad ,
\label{eq:receiver_weights}
\end{equation}
respectively.
Here~$N$ and~$N_{sc}$ are normalization factors,
and~$\Delta_{ss'}$ and~$\Delta_{rr'}$ denote angular distances between source and receiver pairs~$\{s,s'\}$ and~$\{r,r'\}$\,.
The reference angular distances~$\Delta$ and~$\Delta_{sc}$ need to be chosen based on the condition 
numbers of the diagonal weighting matrices defined by Eqns.~(\ref{eq:source_weights}) and~(\ref{eq:receiver_weights}).

@@

We use the same transversely isotropic model parametrization as starting model GLAD-M15.
Such a model is described by the five Love parameters $A$, $C$, $L$, $N$, and $F$~\citep{Love27},
or, alternatively, using the mass density~$\rho$, in terms of the wavespeeds~$\alpha_v=\sqrt{C/\rho}$, $\alpha_h=\sqrt{A/\rho}$, $\beta_v=\sqrt{L/\rho}$, $\beta_h=\sqrt{N/\rho}$ and the dimensionless parameter $\eta=F/(A-2L)$~\citep{PREM,DT98}.
Assuming the radial anisotropy is due to shear anisotropy, these five parameters
may be further reduced to four by introducing the bulk sound speed,
$c=\sqrt{\kappa/\rho}$\,.
Therefore, the final four parameters are $c$, $\beta_v$, $\beta_h$, and $\eta$.
Transverse isotropy is confined to the upper mantle; the lower mantle is assumed to be isotropic.

@@

The observed seismograms need to be compared to corresponding synthetic seismograms
for the purpose of making measurements.
The forward simulations are based on the global spectral-element solver
SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02a}, and take a CMT solution, a relevant list
of stations, and the current earth model as input.
The solver is GPU accelerated, and the simulations are performed on the Cray supercomputer ``Titan''
at the OLCF.
To simulate 120~min seismograms with a shortest period of 17~s on 384 NVIDIA
Tesla K20X GPUs takes approximately 10~min of wall clock time. {\color{red} Wenjie: is that correct?}

@@

As illustrated in Fig.~\ref{fig:preprocess_workflow}, the preprocessing workflow
includes the following phases.
\begin{enumerate}
  \item Signal processing to remove the instrument response from observed data
    to recover ground displacement using ObsPy~\citep{obspy2010}. Both observed and synthetic data are bandpass
    filtered, and the horizontal components are rotated to obtain the radial and transverse components of motion.
  \item Window selection on a pair of
    observed and synthetic seismograms. Pyflex (a Python version
    of FLEXWIN by \citet{krischer2015}) is
    used to automatically generate windows where observed and
    synthetic data are sufficiently close to make measurements based on user defined
    criteria.
  \item Cross-correlation traveltime or multi-taper phase measurements in selected windows.
  \item Window sorting and cleaning based on statistical analyses of all measurements to eliminate outliers.
  \item Preliminary adjoint source construction based on the sorted windows.
  \item Calculation and assignment of weights, as discussed in Section~\ref{section:misfit}.
  \item Construction of the final, properly weighted, adjoint sources.
\end{enumerate}

@@

Collectively,
the adjoint simulations are the most expensive stage of the workflow. 
Adjoint simulations take the adjoint sources as input, and generate Fr\'echet
derivatives of the four model parameters as output.
The computational cost of one adjoint simulation is roughly twice ($\sim25$~min) that of
a forward simulation, since the forward wavefield is recalculated for convolution with
the adjoint wavefield during the adjoint simulation.
Using this procedure,
both the forward and adjoint wavefield are calculated in forward time,
and attenuation is accurately taken into account in both simulations.

The calculation of Fr\'echet derivatives requires
access to snapshots of the forward wavefield as part of the parsimonious storage
algorithm developed by~\cite{KoXiBoPeSaLiTr16},
with rapid I/O facilitated by ADIOS~\citep{liu2014hello}.
For the current simulation setup,
this requires about 1~TB of storage per earthquake,
so for 1,480 earthquakes this adds up to 1.5~PB.
This volume of data is generated during~$\sim6$~hours of simulations.
Based on our experience, ADIOS is capable of achieving~$\sim120$~GB/s
of sustained I/O on OLCF resources.
Given that typical write speeds for modern hard disks are~$\sim100$~MB/s,
it would be extremely difficult to carry out global adjoint tomography without the ADIOS library.

@@

Starting model GLAD-M15 was constructed using a database of 253 earthquakes.
For iterations 15--17 of the inversion we used an expanded database of 520 events.
Our focus was to validate and test our software and workflow before scaling up
to a larger database of 1,040 events.
For these iterations we used three period bands, namely,
17--40~s, 40--100~s, and 90--250~s,
and we used a nonlinear conjugate
gradient method to update the model.

@@

The misfit reduction for 17--40~s body waves (Figs.~\ref{fig:misfit}b--d) tapers off by
iteration~21, prompting us to add more earthquakes and change the weighting strategy again by reintroducing 40--100~s surface waves.

@@

In this section we discuss model GLAD-M25 in detail.
We begin with a global overview of the model before concentrating on
specific geographical regions.
In this paper we focus predominantly on isotropic shear and compressional wavespeed variations.
We conclude by highlighting various slabs and plumes in the model.
Vertical cross sections are plotted relative to the spherical average of GLAD-M25,
as discussed in Appendix~\ref{sec:1Dmodel}.
For plotting purposes and use in other applications,
an expansion of the model in spherical harmonics and radial B-splines is
discussed in Appendix~\ref{sec:shanalysis}.

@@

The deployment of USArray has dramatically increased data coverage across the
continental United States,
and yet despite this tremendous increase in data coverage, there is not as much overlap between different models as one might anticipate.
In this section, we compare GLAD-M25 in this region 
with two global models, S362ANI$+$M and S40RTS, and two regional models,
US22~\citep{zhu2017radial} and SL2013NA~\citep{schaeffer2014imaging}.
US22 is a radially anisotropic model based on adjoint tomography using
USArray data from 180 regional earthquakes using 15--50~s
body waves and 25--150~s surface waves.
SL2013NA is a global upper-mantle shear wavespeed model based on multimode
surface waveform tomography primarily focused on North America.

@@

In the 200--400~km depth range, we observe a high wavespeed
anomaly within the Gulf of Mexico, which coincides spatially with the deepest
bathymetry and corresponds to a portion of ancient oceanic
lithosphere~\citep{muller2008, schaeffer2014imaging}.
A remnant of the Juan de Fuca plate,
with a high wavespeed footprint, is visible at depths of 300~km and 400~km,
where SL2013NA shows a much stronger anomaly.

@@

In the Eastern Mediterranean, there is a distinct fast anomaly beneath the 
Dinarides Mountains, separating the Adria plate from the Pannonian Basin,
indicating subduction of the Adria plate beneath the Eurasian plate.
This anomaly gets sharper at 600~km depth.
Its southern part interacts with the Hellenic slab, which penetrates the mantle
transition zone and extends below 1,000~km in our model.
We discuss the Hellenic Arc further in Section~\ref{section:slabs}.
The Pannonian Basin is characterized by a low wavespeed
anomaly at depths from 100~km to 250~km.
In this depth range we also see slow wavespeeds beneath Anatolia,
stronger than in the two other global models.

@@

In the south,
Scotia Arc subduction is very distinct in GLAD-M25 at all depths,
but barely observable in other models.
This is probably a consequence of coverage provided by events in the region (see Fig.~\ref{fig:event_1480}).
To the north,
Caribbean subduction is clearly discernible in model GLAD-M25 and the two $V_\textrm{P}$ models.

@@

In this section we highlight various subduction systems on Earth.
In Fig.~\ref{fig:subd} we compare GLAD-M25~($V_\textrm{P}$) with two compressional wavespeed models,
namely, GAP-P4~\citep{fukao2013subducted} and UU-P07~\citep{van2018atlas}.
Fig.~\ref{fig:subd}(a) features the Aegean subduction zone. All models show a slab penetrating into the lower mantle beyond a depth of 1,000~km.
Fig.~\ref{fig:subd}(b) shows the South American slab, which, in this cross section, ponds in the shallow lower mantle in all three models, before sinking all the way to the CMB.
Figs.~\ref{fig:subd}(c) and~(d) show cuts across the ancient Farallon slab, which penetrates deeply into the lower mantle.
At depths greater than 1,000~km, 
we see a very strong expression of the slab in model GLAD-M25, which is much weaker in the two P models.
The difference may be attributed to increased data coverage thanks to USArray, as well as the use of finite-frequency Fr\'echet derivatives.
Finally, Fig.~\ref{fig:subd}(e) shows subduction beneath the Himalayas.

@@

\begin{acknowledgments}
This research used resources of the Oak Ridge Leadership Computing Facility,
which is a DOE Office of Science User Facility supported under contract DE-AC05-00OR22725.
Additional computational resources were provided by the Princeton Institute
for Computational Science \& Engineering (PICSciE).
We acknowledge IRIS ({\tt iris.edu}) and ORFEUS ({\tt orfeus-eu.org}) for
providing the data used in this study.
We thank Ryan Modrak, Ridvan \"{O}rsvuran, Frederik J. Simons, and James Smith for fruitful discussions,
and Caio Ciardelli for implementing the spherical harmonic model expansion.
The open source spectral-element software package SPECFEM3D\_GLOBE and
the seismic measurement software package FLEXWIN used for this article are
 freely available via the Computational Infrastructure for Geodynamics
 (CIG; {\tt geodynamics.org}). This research was supported by NSF grant~1644826.
\end{acknowledgments}
